---
title: "2019 GoA CTD Data "
author: "Brett Johnson"
date: '`r date()`'
output:
 html_document:
   theme: cosmo
   number_sections: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)

library(googledrive)
library(tidyverse)
library(lubridate)
library(readxl)
library(here)
library(parsedate)
```

- Download Data

```{r download data}

sheet2 <- read_csv(here("original_data", "Data_IYS_conbined_Final-Sheet2.csv"))

```

- Change date to ISO 8601 format (eg. `r format_iso_8601(as.POSIXct(Sys.time(), format = "%Y-%m-%d %H:%M%:S", tz="Asia/Kamchatka"))`) by adding together the year, month, day, and shiptime columns. 

```{r Date ISO 8601}
sheet2 <- sheet2 %>%
  mutate(eventDate_text = str_c(YEAR, MONTH, DAY, `TIME(ship time)`, `MIN(ship time)`, sep="-"),
         eventDate = ymd_hm(eventDate_text, tz = "Asia/Kamchatka")) %>%
  mutate(eventDate = format_iso_8601(as.POSIXct(eventDate,
                                                format = "%Y-%m-%d %H:%M%:S",
                                                tz="Asia/Kamchatka")),
         eventDate = str_replace(eventDate, "\\+00:00", "Z")
  ) %>% 
  select(-eventDate_text)
```

- The longitude was recorded as positive values, however, after QC and cross-reference to other data recorded during the same cruise, it is clear that the values should be negative.

```{r}
sheet2$LON <- -sheet2$LON
```

- Re-write column names for clarity

```{r}
sheet2 <- sheet2 %>% 
  select(eventDate, NO.Trawl:DEPTH,
    "seabird_sea_water_temperature" = `TEM_S`,
    "rinko_sea_water_temperature" = `TEM_R`,
    "rinko_sea_water_practical_salinity" = `SAL_R`,
    "seabird_sea_water_practical_salinity" = `SAL_S`,
    pH,
    "concentration_of_oxygen" = `O2 [ml/l]`,
    "sea_water_electrical_conductivity" = `Cond. [mS/cm]_R`,
    "sea_water_density" = `Density [kg/m^3]_R`,
    "sea_water_sigma_t" = `SigmaT [ ]_R`,
    "chlorophyll_flu" = `Chl-Flu. [ppb]_R`,
    "chlorophyll_a" = `Chl-a [ug/l]_R`,
    "turbidity" = `Turb-M [FTU]_R`,
    "dissolved_oxygen" = `DO [mg/l]_R`,
    "battery_voltage" = `Batt. [V]_R`,
    "BOD5" = `BOD5[ml/l]`,
    "dissolved_oxygen_saturation" = `DO [%]_R`,
    "EC25" = `EC25 [uS/cm]_R`
    )

```

```{r}
write_csv(sheet2, here("standardized_data", "IYS_2019_CTD.csv"))
```

